### 2017-12-12 Paper/main.tex

\section{Evidence and findings}
After 930 rounds, that is we run the sequence for all the stocks in the portfolio we get the following conclusion:
\begin{itemize}
    \item the model out perform the naive algorithm
    \item the model failed to predict in a consistent way whether the price was going up or down
    \item either the models alone failed to do so 
\end{itemize}
Therefore we can conclude that such model didn't gave any competitive advantage in terms of profit and loss.

@@

The writer of this article hope that many other researchers will try to cast some light above this hybrd methodology in order to develop a better process for such modelling.

@@

>>>>

\section{Evidence and findings}
After 930 rounds, that is we run the sequence for all the stocks in the portfolio, we got the following conclusion:
\begin{itemize}
    \item the model out perform the naive algorithm;
    \item the model failed to predict in a consistent way whether the price was going up or down;
    \item either the models alone failed to do so;
    \item the plain ARIMA performed purely in comparison with the hybrid model.
\end{itemize}

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth, ]{Paper/images/PL_plot.png}
    \caption{Plot of the aggregate P/L per stock}
    \label{pl_portfolio}
\end{figure}

Therefore we can conclude that such model didn't gave any competitive advantage in terms of profit and loss.

In order to be sure of the forecasting prediction we computed the confusion matrix of each model and we get the following information:
\begin{itemize}
    \item the model out perform the naive algorithm;
    \item the model failed to predict in a consistent way whether the price was going up or down;
    \item either the models alone failed to do so;
    \item the plain ARIMA performed purely in comparison with the hybrid model.
\end{itemize}

@@

The writer of this article hope that many other researchers will try to cast some light above this hybrid methodology in order to develop a better process for such modelling.

@@

\newpage
\begin{figure}
    \centering
    \includegraphics[width=1\linewidth, ]{Paper/images/NN_plot}
    \caption{Plot of the aggregate P/L per stock}
    \label{nn_portfolio}
\end{figure}
